\Title

### 2023-02-07 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

Through an ecological motion detection task, we study the emergence of spatio-temporal spiking motifs when training a single layer of spiking neurons on a semi-supervised classification task (\seeFig{motion_task}). First, we define the ecological cognitive task the model has to solve with the different datasets it will be tested on. Then, we develop a theoretically defined Heterogeneous Delays in Spiking Neural Network (HD-SNN) model capable of learning heterogenous synaptic delays. We will study the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. This will allow us to show how such a model can provide an efficient solution to the energy/accuracy trade-off. 

>>>>

Through an ecological motion detection task, we study the emergence of spatio-temporal spiking motifs when training a single layer of spiking neurons on a supervised classification task. First, we define the ecological cognitive task the model has to solve with the different datasets it will be tested on. Then, we develop a theoretically defined Heterogeneous Delays in Spiking Neural Network (HD-SNN) model capable of learning heterogenous synaptic delays. We will study the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. This will allow us to show how such a model can provide an efficient solution to the energy/accuracy trade-off. 
